%  article.tex (Version 3.3, released 19 January 2008)
%  Article to demonstrate format for SPIE Proceedings
%  Special instructions are included in this file after the
%  symbol %>>>>
%  Numerous commands are commented out, but included to show how
%  to effect various options, e.g., to print page numbers, etc.
%  This LaTeX source file is composed for LaTeX2e.

%  The following commands have been added in the SPIE class
%  file (spie.cls) and will not be understood in other classes:
%  \supit{}, \authorinfo{}, \skiplinehalf, \keywords{}
%  The bibliography style file is called spiebib.bst,
%  which replaces the standard style unstr.bst.

\documentclass[letter]{spie}  %>>> use for US letter paper
%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
%% \addtolength{\voffset}{9mm}   %>>> moves text field down
%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing

%% Latex documents that need direct input
\input{latex/filesystem/package.tex}        % contains the latex packages
\input{content/frontmatter.tex}             % contains the Title and Autor info
\input{latex/filesystem/fileSetup.tex}      % contains package and variables init.
\input{content/acronym_definition.tex}      % contains the acronims

%% Select inputing only one part of the document
%\includeonly{content/intro/intro}   % the file wihtout .tex
%\includeonly{content/other/other_content}

% \addbibresource{./content/lit_review.bib}
% \addbibresource{./content/biblatex-examples.bib}

\begin{document}

\maketitle

\begin{abstract}
\acresetall  % reset the acronyms from the title (if any)
Malignant melanoma is the most dangerous type of skin cancer, yet it is the most treatable kind of cancer, conditioned to its early diagnosis. 
The early prognosis of melanoma is a challenging task for both clinicians and dermatologists.
In this regard, Computer Aided Diagnosis systems based on machine learning and image processing techniques have been developed to differentiate melanoma lesions from benign and dysplastic nevi in dermoscopic images. 
In such systems, preprocessing of the acquired images such as illumination correction and lesion segmentation are critical tasks and have high impacts on the final results. 
In this paper, we propose a classification framework which does not require prior segmentation of the lesions or illumination correction and is based on sparse coding techniques.
{\color{red}In this paper, we propose to use sparse coding techniques without prior lesion segmentation or illumination correction for melanoma classification.} 
%Our proposed framework considers comparison of three sparse coded features such as SIFT, color histograms and statistics and RGB intensity values with Random Forest classifier. 
Our proposed framework employs Random Forests classifier and sparse representation of three features such as SIFT, color histograms and statistics and RGB intensity values. 
Our experiments on publicly available $PH^{2}$ dataset with 80\% of the data used for training and the rest for testing testing and 10-fold cross-validation revealed that SIFT sparse coded features achieved the highest performance with Sensitivity and Specificity of 100\% and 90.3\% respectively, with dictionary size of 800 atoms and sparsity level of 2. 
The obtained results also shows that the dictionary learned from simple RGB intensity values of dermoscopic images achieved comparative results of 100\% Sensitivity and 71.3\% Specificity with smaller dictionary size of 100 atoms. 
In general the obtained results indicates that dictionary learning techniques can capture strong structure of dermoscopic images and produce discriminant descriptors for classification.
\end{abstract}

%\keywords{KeyWordA, KeyWordB, KeyWordC}
%
%
%%% Incldue the content without .tex extension
%\acresetall  % reset the acronyms from the abstract
%\include*{content/intro/intro}          % the file wihtout .tex
%\include*{content/other/other}
%
%\acknowledgments     %>>>> equivalent to \section*{ACKNOWLEDGMENTS}
%
%This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.
%
%\bibliography{./content/lit_review}   %>>>> bibliography data in report.bib
%\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst

\end{document}

